xxx

### 2018-05-09 Manuscript.Rmd
Auswertung Turnover angepasst und erweitert.

# Introduction {-}
xxx

@@

```{r}
summary(lm(Turnover ~ NTOT2007 + Hoehe + Neig + Expos, data = sites))
```

>>>>

# Introduction {-}

@@

```{r}
tt <- sites %>% gather(Period, Turnover, -aID_STAO, -Elevation,  -Inclination, -Temperature, -Precipitation, -NDEP2010)

summary(lmer(Turnover ~ Period * (Temperature + Precipitation + NDEP2010 + Inclination) +
               (1|aID_STAO), data = tt)) 
summary(lmer(Turnover ~ Period + Temperature + Precipitation + NDEP2010 + Inclination +
               (1|aID_STAO), data = tt))
# Neigung als Mass für Land-use intensity
```
